---
title: "Healthcare_Policies_SCM_Analysis"
output: html_document
date: "2026-02-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Processing

### Import Libraries
```{r}
library(Synth)
library("jsonlite")
library(dplyr)
library(tidyr)
library("ggplot2")
library("survival")
library("survminer")
library(scales)
library(lubridate)
library(readxl)

```

# Load in Data from Excel spreadsheets
```{r}
# Import Excel file with truveta data
T_rates_df <- read_excel(
  path = "Truveta_Prescriptions.xlsx",
  sheet = "Sheet1"   
)
T_rates_df <- as.data.frame(T_rates_df)
T_rates_df <- T_rates_df %>%
  mutate(
    Date = as.Date(paste0(Date, "-01"))  # 2015-01 -> 2015-01-01
  )
T_rates_df <- T_rates_df %>%
  mutate(
    legislation_date = as.Date((legislation_date))
  )
T_rates_df$Virtual_T_Rate <- as.numeric(T_rates_df$Virtual_T_Rate)
T_rates_df$Total_T_Rate <- as.numeric(T_rates_df$Total_T_Rate)

# Import Excel file with SCM covariate data
SCM_df <- read_excel(
  path = "SCM_Dataframe.xlsx",
  sheet = "Sheet1"   
)
SCM_df <- as.data.frame(SCM_df)

# Make all number columns numeric data type
SCM_df <- SCM_df %>%
  mutate(across(4:20, ~ as.numeric(.x)))

# Assign unique number to each state for SCM
SCM_df <- SCM_df %>%
  mutate(state_id = as.integer(factor(state_name)))
```

# Create graphs for treatment states

## States with Restrictive Legislation

### Iowa
```{r}
plot_state <- "Iowa"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

p_IA <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "orangered") +         
  geom_point(size = 2, colour = "orangered3") +  
  geom_vline(xintercept = leg_date,
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) +
                    0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -
                          min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    breaks = seq(min(current_state$Date, na.rm = TRUE),
                 max(current_state$Date, na.rm = TRUE),
                 by = "1 month"),
    labels = function(x) ifelse(month(x) %in% c(1, 7),
                                format(x, "%Y-%m"),
                                "")
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_IA

```

### Louisiana
```{r}
plot_state <- "Louisiana"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

p_LA <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "orangered") +         
  geom_point(size = 2, colour = "orangered3") +  
  geom_vline(xintercept = leg_date,          # vertical line
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  # vertical line label
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) + 0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    date_breaks = "3 months",                        # major tick every 3 mo
    date_labels = "%Y-%m",                           # shown as YYYY-MM
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +  # height / width ratio
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_LA 
```

### Missouri
```{r}
plot_state <- "Missouri"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

p_MO <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "orangered") +         
  geom_point(size = 2, colour = "orangered3") +  
  geom_vline(xintercept = leg_date,          # vertical line
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  # vertical line label
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) + 0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    date_breaks = "3 months",                        # major tick every 3 mo
    date_labels = "%Y-%m",                           # shown as YYYY-MM
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +  # height / width ratio
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_MO
```

### Ohio
```{r}
plot_state <- "Ohio"

current_state <- T_rates_df %>%
  filter(State == plot_state, Date >= as.Date("2016-01-01"))  # Ohio has high outlier in 2015
leg_date <- current_state$legislation_date[1]

p_OH <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "orangered") +         
  geom_point(size = 2, colour = "orangered3") +  
  geom_vline(xintercept = leg_date,          # vertical line
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  # vertical line label
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) + 0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    date_breaks = "3 months",                        # major tick every 3 mo
    date_labels = "%Y-%m",                           # shown as YYYY-MM
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +  # height / width ratio
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_OH

```

### Texas
```{r}
plot_state <- "Texas"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

p_TX <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "orangered") +         
  geom_point(size = 2, colour = "orangered3") +  
  geom_vline(xintercept = leg_date,          # vertical line
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  # vertical line label
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) + 0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    date_breaks = "3 months",                        # major tick every 3 mo
    date_labels = "%Y-%m",                           # shown as YYYY-MM
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +  # height / width ratio
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_TX

```

### Florida
```{r}
plot_state <- "Florida"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

p_FL <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "orangered") +         
  geom_point(size = 2, colour = "orangered3") +  
  geom_vline(xintercept = leg_date,          # vertical line
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  # vertical line label
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) + 0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    date_breaks = "3 months",                        # major tick every 3 mo
    date_labels = "%Y-%m",                           # shown as YYYY-MM
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +  # height / width ratio
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_FL

```

## States with Shield Laws

### California
```{r}
plot_state <- "California"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

p_CA <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "dodgerblue2") +         
  geom_point(size = 2, colour = "dodgerblue4") +  
  geom_vline(xintercept = leg_date,          # vertical line
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  # vertical line label
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) + 0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    date_breaks = "3 months",                        # major tick every 3 mo
    date_labels = "%Y-%m",                           # shown as YYYY-MM
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +  # height / width ratio
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_CA

```

### Maryland
```{r}
plot_state <- "Maryland"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

p_MD <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "dodgerblue2") +         
  geom_point(size = 2, colour = "dodgerblue4") +  
  geom_vline(xintercept = leg_date,          # vertical line
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  # vertical line label
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) + 0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    date_breaks = "3 months",                        # major tick every 3 mo
    date_labels = "%Y-%m",                           # shown as YYYY-MM
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +  # height / width ratio
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_MD

```

### Oregon
```{r}
plot_state <- "Oregon"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

p_OR <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "dodgerblue2") +         
  geom_point(size = 2, colour = "dodgerblue4") +  
  geom_vline(xintercept = leg_date,          # vertical line
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  # vertical line label
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) + 0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    date_breaks = "3 months",                        # major tick every 3 mo
    date_labels = "%Y-%m",                           # shown as YYYY-MM
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +  # height / width ratio
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_OR

```

### Washington
```{r}
plot_state <- "Washington"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

p_WA <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "dodgerblue2") +         
  geom_point(size = 2, colour = "dodgerblue4") +  
  geom_vline(xintercept = leg_date,          # vertical line
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  # vertical line label
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) + 0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    date_breaks = "3 months",                        # major tick every 3 mo
    date_labels = "%Y-%m",                           # shown as YYYY-MM
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +  # height / width ratio
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )

p_WA
```

### Illinois
```{r}
plot_state <- "Illinois"

current_state <- T_rates_df %>%
  filter(State == plot_state)
leg_date <- current_state$legislation_date[1]

library(lubridate)

p_IL <- ggplot(current_state, aes(x = Date, y = Total_T_Rate)) +
  geom_line(size = 1, colour = "dodgerblue2") +         
  geom_point(size = 2, colour = "dodgerblue4") +  
  geom_vline(xintercept = leg_date,
             linetype  = "dashed",
             colour    = "gray37",
             size      = 0.8) +
  annotate("text",
           x      = leg_date,
           y      = min(current_state$Total_T_Rate, na.rm = TRUE) +
                    0.15*(max(current_state$Total_T_Rate, na.rm = TRUE) -
                          min(current_state$Total_T_Rate, na.rm = TRUE)),
           label  = "Legislation Date",
           vjust  = 1.4,
           angle  = 90,
           colour = "gray37",
           size   = 3) +
  scale_x_date(
    breaks = seq(min(current_state$Date, na.rm = TRUE),
                 max(current_state$Date, na.rm = TRUE),
                 by = "1 month"),
    labels = function(x) ifelse(month(x) %in% c(1, 7),
                                format(x, "%Y-%m"),
                                "")
  ) +
  labs(
    title = paste("Normalized T Prescription Rates in", plot_state),
    x = "Date",
    y = "T Prescription Rate"
  ) +
  theme(aspect.ratio = 4/10) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold"),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )


p_IL

```

### Subplots for all states
```{r}
(p_IA | p_LA | p_MO | p_OH | p_TX | p_FL) /
(p_CA | p_MD | p_OR | p_WA | p_IL)
```
# Run Synthetic Control on Treatment States

## Function Wrapper
```{r}
run_scm <- function(treated_state,
                   control_state_ids,
                   interruption_year,
                   data) {
  
  treated_state_id <- data %>%
  filter(`state_name` %in% c(treated_state)) %>%
  distinct(state_id) %>%
  pull(state_id)

  # vectors for time periods 
  time_predictors_prior <- 2019:(interruption_year - 1)
  time_optimize_ssr     <- 2019:interruption_year
  time_plot             <- 2019:2025   

  dataprep_out <- dataprep(
    foo = data,
    predictors = c(
      "Total People In Truveta", 
      "Trans People In Truveta", 
      "Uninsured raw value",
      "Median Household Income raw value",
      "% Below 18 Years of Age raw value",
      "% 65 and Older raw value",
      "% Non-Hispanic Black raw value",
      "% American Indian or Alaska Native raw value",
      "% Asian raw value",
      "% Native Hawaiian or Other Pacific Islander raw value",
      "% Hispanic raw value",
      "% Non-Hispanic White raw value",
      "% Female raw value",
      "Fraction_Medicaid_Medicare"
    ),
    predictors.op = "mean",
    dependent = "Total T Prescriptions",
    unit.variable = "state_id",
    time.variable = "Year",
    special.predictors = NULL,
    treatment.identifier = treated_state_id,
    controls.identifier = control_state_ids,
    time.predictors.prior = time_predictors_prior,
    time.optimize.ssr = time_optimize_ssr,
    unit.names.variable = "State Abbreviation",
    time.plot = time_plot
  )

  synth_out <- synth(dataprep_out)
  #list(dataprep = dataprep_out, synth = synth_out)
  
  # Predictor weights (solution.v) with predictor names
  #v <- synth_out$solution.v
  #cat("\nPredictor weights:\n")
  #print(v)  # names(v) are predictor row names of X-matrix

  # Control weights (solution.w) with state names
  #w <- synth_out$solution.w              # matrix: rows = control units
  #w_vec <- as.numeric(w)
  #names(w_vec) <- rownames(w)            # should be control state names/ids
  #cat("\nControl unit weights:\n")
  #print(round(w_vec, 3))

  path.plot(
  synth.res    = synth_out,
  dataprep.res = dataprep_out,
  tr.intake    = interruption_year,                     # treatment year
  Ylab         = "Total T Prescriptions",
  Xlab         = "Year",
  Main         = paste(treated_state, " vs Synthetic Control")
)
}
```


### Create Control group
```{r}
control_states <- SCM_df %>%
  filter(`State Abbreviation` %in% c("MI", "WI", "PA", "VA", "HI", "AK", "NC")) %>%
  distinct(state_id) %>%
  pull(state_id)
```

## Run SCM and Plot for each state

## Restrictive Sates 

### Iowa
```{r}
state_to_use <- "Iowa"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

### Louisiana
```{r}
state_to_use <- "Louisiana"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

### Missouri
```{r}
state_to_use <- "Missouri"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

### Ohio
```{r}
state_to_use <- "Ohio"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date), Date >= as.Date("2016-01-01")) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

### Texas
```{r}
state_to_use <- "Texas"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

### Florida
```{r}
state_to_use <- "Florida"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

## Shield States

### California
```{r}
state_to_use <- "California"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

### Maryland
```{r}
state_to_use <- "Maryland"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

### Oregon
```{r}
state_to_use <- "Oregon"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

### Washington
```{r}
state_to_use <- "Washington"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```

### Illinois
```{r}
state_to_use <- "Illinois"

leg_year <- T_rates_df %>%
  filter(State == state_to_use, !is.na(legislation_date)) %>%
  mutate(legislation_date = as.Date(legislation_date)) %>%
  distinct(State, legislation_date) %>%   # just in case multiple rows
  pull(legislation_date) %>%
  year()

run_scm(state_to_use, control_states, leg_year, SCM_df)
```